modelStudio - R & Python examples

### 2021-01-07 inst/doc/ms-perks-features.Rmd
version 2.1.1

The `modelStudio()` function computes various (instance and dataset level) model explanations 
and produces a customisable dashboard, which consists of multiple panels for plots with their
short descriptions. Easily save the dashboard and share it with others. Tools for
[Explanatory Model Analysis](https://pbiecek.github.io/ema/) unite with tools for Exploratory Data Analysis 
to give a broad overview of the model behavior.

@@

Pass data points to the `new_observation` parameter for instance explanations
such as [Break Down](https://pbiecek.github.io/ema/breakDown.html),
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Ceteris Paribus](https://pbiecek.github.io/ema/ceterisParibus.html) Profiles.
Use `new_observation_y` to show their true labels.

@@

- `N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles (default is `300`). 
- `N_fi` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `10*N`).
- `B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) (default is `10`).
- `B_fi` is a number of permutation rounds used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `B`).

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema/)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

>>>>

The `modelStudio()` function computes various (instance and dataset level) model explanations 
and produces a customisable dashboard, which consists of multiple panels for plots with their
short descriptions. Easily save the dashboard and share it with others. Tools for
[Explanatory Model Analysis](https://ema.drwhy.ai/) unite with tools for Exploratory Data Analysis 
to give a broad overview of the model behavior.

@@

Pass data points to the `new_observation` parameter for instance explanations
such as [Break Down](https://ema.drwhy.ai/breakDown.html),
[Shapley Values](https://ema.drwhy.ai/shapley.html) and
[Ceteris Paribus](https://ema.drwhy.ai/ceterisParibus.html) Profiles.
Use `new_observation_y` to show their true labels.

@@

- `N` is a number of observations used for calculation of
[Partial Dependence](https://ema.drwhy.ai/partialDependenceProfiles.html)
and [Accumulated Dependence](https://ema.drwhy.ai/accumulatedLocalProfiles.html) Profiles (default is `300`). 
- `N_fi` is a number of observations used for calculation of
[Feature Importance](https://ema.drwhy.ai/featureImportance.html) (default is `10*N`).
- `B` is a number of permutation rounds used for calculation of
[Shapley Values](https://ema.drwhy.ai/shapley.html) (default is `10`).
- `B_fi` is a number of permutation rounds used for calculation of
[Feature Importance](https://ema.drwhy.ai/featureImportance.html) (default is `B`).

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain, and Examine Predictive Models.](https://ema.drwhy.ai/)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

### 2021-01-07 inst/doc/ms-r-python-examples.Rmd
version 2.1.1

```{r eval = FALSE}
# packages for explainer objects
install.packages("DALEX")
install.packages("DALEXtra")

# update main dependencies
install.packages("ingredients")
install.packages("iBreakDown")
```

### mlr [dashboard](https://modeloriented.github.io/modelStudio/mlr.html)

@@

### mlr3 [dashboard](https://modeloriented.github.io/modelStudio/mlr3.html)

@@

### xgboost [dashboard](https://modeloriented.github.io/modelStudio/xgboost.html)

@@

### caret [dashboard](https://modeloriented.github.io/modelStudio/caret.html)

@@

### h2o [dashboard](https://modeloriented.github.io/modelStudio/h2o.html)

@@

### parsnip [dashboard](https://modeloriented.github.io/modelStudio/parsnip.html)

@@

@@

```{bash, eval=FALSE, engine="sh"}
# package for Explainer object
pip3 install dalex --force
```

@@

```{r eval = FALSE}
# package for pickle load
install.packages("reticulate")

# update main dependencies
install.packages("ingredients")
install.packages("iBreakDown")
```

### scikit-learn [dashboard](https://modeloriented.github.io/modelStudio/scikitlearn.html)

@@

### lightGBM [dashboard](https://modeloriented.github.io/modelStudio/lightgbm.html)

@@

# create an explainer for the model
explainer = dx.Explainer(model, data=X_test, y=y_test, label='lightGBM')

@@

### keras/tensorflow [dashboard](https://modeloriented.github.io/modelStudio/keras.html)

@@

#! add blank create_architecture function before load !
py_run_string("
def create_architecture():
    return True
")

@@

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

>>>>

```{r eval = FALSE}
# packages for the explainer objects
install.packages("DALEX")
install.packages("DALEXtra")
```

### mlr [dashboard](https://modelstudio.drwhy.ai/mlr.html)

@@

### mlr3 [dashboard](https://modelstudio.drwhy.ai/mlr3.html)

@@

### xgboost [dashboard](https://modelstudio.drwhy.ai/xgboost.html)

@@

### caret [dashboard](https://modelstudio.drwhy.ai/caret.html)

@@

### h2o [dashboard](https://modelstudio.drwhy.ai/h2o.html)

@@

### parsnip [dashboard](https://modelstudio.drwhy.ai/parsnip.html)

@@

### tidymodels [dashboard](https://modelstudio.drwhy.ai/tidymodels.html)

```{r eval=FALSE}
# load packages and data
library(tidymodels)
library(DALEXtra)
library(modelStudio)

# tidymodels fit takes target as factor
train$survived <- as.factor(train$survived)

# fit a model
rec <- recipe(survived ~ ., data = train) %>%
       step_normalize(fare)

clf <- rand_forest(mtry = 2) %>%
       set_engine("ranger") %>%
       set_mode("classification")

wflow <- workflow() %>%
         add_recipe(rec) %>%
         add_model(clf)

model <- wflow %>% fit(data = train)

# create an explainer for the model
explainer <- explain_tidymodels(model,
                                data = test,
                                y = test$survived,
                                label = "tidymodels")

@@

```{bash, eval=FALSE, engine="sh"}
# package for the Explainer object
pip install dalex -U
```

@@

```{r eval = FALSE}
# package for pickle load
install.packages("reticulate")
```

### scikit-learn [dashboard](https://modelstudio.drwhy.ai/scikitlearn.html)

@@

### lightgbm [dashboard](https://modelstudio.drwhy.ai/lightgbm.html)

@@

# create an explainer for the model
explainer = dx.Explainer(model, data=X_test, y=y_test, label='lightgbm')

@@

### keras/tensorflow [dashboard](https://modelstudio.drwhy.ai/keras.html)

@@

#! add blank create_architecture function before load !
py_run_string('
def create_architecture():
    return True
')

@@

-------------------------------------------------------------------

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain, and Examine Predictive Models.](https://ema.drwhy.ai/)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)
